---
title: "Lab 18 — ETS, Accuracy & ARIMA Bridge"
subtitle: "Time Series Analysis (BDBA) · optional session notebook"
author: "Prof. Dae-Jin Lee (daelee@faculty.ie.edu)"
output:
  html_document:
    toc: true
    toc_float: true
---


## Learning goals

By the end of this lab you should be able to:

- build a clean train/test split for a `tsibble`;
- compare ETS and a seasonal naïve forecast with `accuracy()`;
- use differencing displays to motivate an ARIMA order;
- report hold-out RMSE/MAE without comparing AICc across model families.

## 1. Setup

```{r}
library(fpp3)
```

## 2. Series and split

```{r}
beer <- aus_production |>
  select(Quarter, Beer) |>
  filter(!is.na(Beer))

beer_train <- beer |> filter(Quarter <= max(Quarter) - 8)
beer_test  <- beer |> filter(Quarter >  max(Quarter) - 8)

beer |> autoplot(Beer) + labs(title = "Beer production", y = "Megalitres")
```

How many quarters are in train vs test?

```{r}
# Your code here
```

## 3. ETS and seasonal naïve

```{r}
# Fit ETS(Beer) and SNAIVE(Beer) on beer_train
# Forecast the test horizon and call accuracy()
# Your code here
```

## 4. Differencing and ACF/PACF

```{r}
beer_train |> gg_tsdisplay(Beer, plot_type = "partial")
```

```{r}
# Plot gg_tsdisplay on difference(Beer)
# Your code here
```

## 5. ARIMA

```{r}
# Manual candidate + ARIMA(Beer) auto; compare AICc; test accuracy
# Your code here
```

## 6. Residuals

```{r}
# gg_tsresiduals for your preferred model
# Your code here
```

## DELIVERABLE

Render this `lab.qmd` to HTML. Include a short markdown paragraph:

1. Winning model on test RMSE (and MAE if different).
2. Whether you would use $d=1$ and why.
3. Any residual ACF concern.

Submit the HTML (or `.qmd` + HTML) per LMS instructions.
