---
title: "Lab 19 — Final Course Review Bake-off"
subtitle: "Time Series Analysis (BDBA) · optional session notebook"
author: "Prof. Dae-Jin Lee (daelee@faculty.ie.edu)"
output:
  html_document:
    toc: true
    toc_float: true
---


## Learning goals

- Run a three-way bake-off: seasonal naïve, ETS, ARIMA.
- Compare models on a hold-out with RMSE and MAE.
- Write a short exam-style justification of your pick.

```{r}
library(fpp3)
```

## Data

```{r}
beer <- aus_production |>
  select(Quarter, Beer) |>
  filter(!is.na(Beer))

train <- beer |> filter(Quarter <= max(Quarter) - 8)
test  <- beer |> filter(Quarter >  max(Quarter) - 8)

beer |> autoplot(Beer)
```

## Models

```{r}
# Fit SNAIVE(Beer), ETS(Beer), ARIMA(Beer) on train
# Forecast h = nrow(test); accuracy()
# Your code here
```

## Diagnostics

```{r}
# Residuals for your preferred model
# Your code here
```

## DELIVERABLE

Render to HTML. Include:

1. Accuracy table (RMSE, MAE).
2. A paragraph (≤120 words) as if answering: “Which method would you recommend and why?”
3. One residual caveat.

Submit per LMS instructions.
