---
title: "Lab 02 — Time Series Graphics"
subtitle: "Time Series Analysis (BDBA) · optional session notebook"
author: "Prof. Dae-Jin Lee (daelee@faculty.ie.edu)"
output:
  html_document:
    toc: true
    toc_float: true
---



## Learning goals

- build time, seasonal, subseries, and lag plots;
- describe trend vs season in words.

```{r}
library(fpp3)
```

## 1. Time plot

```{r}
aus_production |> autoplot(Beer)
```

## 2. Seasonal tools

```{r}
aus_production |> gg_season(Beer, labels = "both")
aus_production |> gg_subseries(Beer)
```

## 3. Lag plot

```{r}
aus_production |> gg_lag(Beer, geom = "point")
```

## 4. Tourism stretch

Victoria has many regions, so plotting them together creates a spaghetti chart.
First aggregate to one state-level series; then optionally facet a few regions.

```{r tourism-state, fig.width=8, fig.height=4}
vic_holiday <- tourism |>
  filter(Purpose == "Holiday", State == "Victoria") |>
  index_by(Quarter) |>
  summarise(Trips = sum(Trips), .groups = "drop")

vic_holiday |>
  autoplot(Trips) +
  labs(
    title = "Victoria holiday trips (all regions summed)",
    y = "Trips"
  )
```

```{r tourism-regions, fig.width=9, fig.height=6}
tourism |>
  filter(
    Purpose == "Holiday",
    Region %in% c("Melbourne", "Great Ocean Road", "High Country", "Phillip Island")
  ) |>
  autoplot(Trips) +
  facet_wrap(vars(Region), scales = "free_y", ncol = 2) +
  guides(colour = "none") +
  labs(title = "Selected Victoria holiday regions", y = "Trips")
```

## DELIVERABLE

Which quarter looks highest for Beer? Support with a plot.

